### 2025-04-17 docs/Homeownership_BankOfMomAndDad.tex
Updated behind regressions
Adding the prelim maintaing ownership res.

The sample is limited to the first time a household is observed as owners, and the control variables are the same as in the previous regression:
\begin{equation*}
Behind_i = \beta_1 \ln(Wealth)_{p(i),t-2} + \beta_2 \ln(Inc_{i,t-2}) + \beta_3 \ln(NetWorth_{i,t-2}) + \mathbf{\gamma}{X_{i,t}} + \varepsilon_{i}.
\end{equation*}
In Column 2 of Table \ref{tab:hypo}, the outcome variable is whether households are behind on the mortgage payments the first time they are observed as owners. Parental wealth in the period before purchase decreases the probability that a household will ever be behind: A 1\% increase in parental wealth decreases the probability of being behind by 0.016 percentage points and is significant at the 1\% level. Parental wealth has a larger effect than the child's net worth. In Column 3, the outcome variable is whether first-time homeowners will ever be observed to be behind on their mortgage, and coefficients and significance levels are virtually unchanged. The sample size increases in these regressions, since households who bought before 2009 are now included.
\begin{table}
	\begin{threeparttable}
		\caption{Housing Choices and Parental Wealth}
		\label{tab:hypo}
		\small 
				\input{../tabfig/regr/hypoII.tex}

@@

>>>>

The sample is limited to the first time a household is observed as owners, and the control variables are the same as in the previous regression:
\begin{equation*}
Behind_i = \beta_1 \ln(Wealth)_{p(i),t-2} + \beta_2 \ln(Inc_{i,t-2}) + \beta_3 \ln(NetWorth_{i,t-2}) + \mathbf{\gamma}{X_{i,t}} + \varepsilon_{i}.
\end{equation*}
In Column 2 of Table \ref{tab:hypo}, the outcome variable is whether households are behind on the mortgage payments the first time they are observed as owners. Parental wealth in the period before purchase decreases the probability that a household will ever be behind: A 1\% increase in parental wealth decreases the probability of being behind by 0.016 percentage points and is significant at the 1\% level. Parental wealth has a larger effect than the child's net worth. In Column 3, the outcome variable is whether first-time homeowners will ever be observed to be behind on their mortgage, and coefficients and significance levels are virtually unchanged. The sample size increases in these regressions, since households who bought before 2009 are now included.
\begin{table}
	\begin{threeparttable}
		\caption{Housing Choices and Parental Wealth}
		\label{tab:hypo}
		\small 
				\input{../tabfig/regr/hypoII_short.tex}

@@

\subsubsection{Households with Wealthier Parents Are More Likely to Remain Homeowners}
\textcolor{red}{!! [[rewrite this]] !!}
Perhaps surprisingly, homeownerhsip is not a `permanent' state, and in fact a growing literature is focusing on the exit from homeownership... (Bond \& Eriksen, ... other papers)\dots

First, I plot the share of homeowners who are homeowners in period $t+\Delta$. The results are striking, among first-time owners (i.e., households whose first observation was as renters and then the first time they were observed as an owner), about 15\% are renting two years later and 20\% are renting after 4 years. For all owners (i.e., the sample includes all households who are observed as owners, in any period), there is a marked decrease though it is more muted, after four years about 10\% of all owners will be renting.

Which variable predict the transition out of ownership? I run similar regresions to the previous sections, for various lead lengths, and plot the coefficient for household net worth and parental wealth. While the coefficient intervals are overlapping, we see a strikin result: at every horizon, a 1\% increase in parental wealth is associated with a larger decrease in the probability of transitioning out of owning.

\begin{figure}[tb]
	\captionsetup[subfigure]{aboveskip=-1pt}
	\caption{Mainting Homeownership}\label{fig:homeowner_exit}
	\begin{subfigure}{0.33\textwidth}%
		\caption{Exit Out of Ownership}\label{fig:owner_hazard}%
		\includegraphics[width=\textwidth]{../tabfig/descr/PSID_ownerexit.pdf}% 
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.33\textwidth}%
		\caption{All Owners}\label{fig:coef_allowner}%
		\includegraphics[width=\textwidth]{../tabfig/descr/PSID_coefowner.pdf}% 
	\end{subfigure}%
	\hfill
	\begin{subfigure}{0.33\textwidth}%
		\caption{First-Time Owners}\label{fig:coef_ftowner}%
		\includegraphics[width=\textwidth]{../tabfig/descr/PSID_coefftowner.pdf}% 
	\end{subfigure}%
	\hfill

	\caption*{\footnotesize \textit{Notes:} \textcolor{red}{write this footnote.}}
\end{figure}
